\cvsection{Educational background}

\begin{cventries}
\cventry{KU Leuven}{Doctoral Programme in Biomedical Science (PhD) in Computational Neuroscience}{Leuven, Belgium}{Sep. 2018 - May 2023}
{\begin{cvitems}\item Cognitive and Molecular Neuroscience
\item PhD Thesis: Finger Movement Decoding: From Source-Localisation to Tensor Regression Modelling
\end{cvitems}
}

\cventry{KU Leuven}{Advanced Master of Science in Engineering (M.Sc.) in Artificial Intelligence}{Leuven, Belgium}{Sep. 2017 - Jul. 2019}
{\begin{cvitems}\item Engineering and Computer Science
\item Thesis: An Information Theoretical Approach to EEG Source-Reconstructed Connectivity (on Github)
\end{cvitems}
}

\cventry{KU Leuven}{Honoursprogramme of the Faculty of Engineering Science (Research Track)}{Leuven, Belgium}{Sep. 2016 - Oct. 2018}
{\begin{cvitems}\item Research Assistant: design of type-\&-effect system for Eff  based on row polymorphism
\item Research Assistent: efficient compilation of algebraic effect handlers (in Eff)
\end{cvitems}
}

\cventry{KU Leuven}{Master of Science in Engineering (M.Sc.) in Computer Science (Burgelijk Ingenieur - ir.)}{Leuven, Belgium}{Sep. 2016 - Sep. 2018}
{\begin{cvitems}\item Artificial Intelligence \& Theoretical Computer Science
\item Thesis: Algebraic Subtyping for Algebraic Effects and Handlers (on Github)
\end{cvitems}
}

\cventry{The University of Manchester}{Business Summer School: United in Manchester (0739)}{Manchester, UK}{Jul. 2015 - Aug. 2015}
{\begin{cvitems}\item International Business
\end{cvitems}
}

\cventry{UHasselt}{Bachelor of Science (B.Sc.) in Computer Science}{Hasselt, Belgium}{Sep. 2013 - Jul. 2016}
{\begin{cvitems}\item Physics and General courses
\item Thesis: Machine learning techniques for flow-based network intrusion detection systems (on Github)
\end{cvitems}
}


\end{cventries}
