\cvsection{Work \& Research Experience}

\begin{cventries}
\cventry{KU Leuven}{Postdoc}{Leuven, Belgium}{May 2023 - Current}
{\begin{cvitems}\item Project: "Sign Language Alphabet decoding from intracranial brain activity"
\item Promoter: Prof. Marc van Hulle
\item Group:  Computational Neuroscience, Laboratory for Neuro-and Psychophysiology, KU Leuven
\end{cvitems}
}

\cventry{KU Leuven}{Phd Candidate (FWO-Aspirant Fellowship)}{Leuven, Belgium}{Oct. 2018 - May 2023}
{\begin{cvitems}\item Project: "Finger Movement Decoding: From Source-Localisation to Tensor Regression Modelling"
\item Promoter: Prof. Marc van Hulle
\item Group:  Computational Neuroscience, Laboratory for Neuro-and Psychophysiology, KU Leuven
\end{cvitems}
}

\cventry{KU Leuven}{Student Job: Creating System Identification course}{Leuven, Belgium}{Sep. 2017 - Sep. 2018}
{\begin{cvitems}\item Faculty of Engineering Science: ESAT (Electrical Engineering)
\item Research group: STADIUS
\end{cvitems}
}

\cventry{KU Leuven}{Research Assistant: design of type-\&-effect system for Eff  based on row polymorphism}{Leuven, Belgium}{Apr. 2017 - Oct. 2017}
{\begin{cvitems}\item Faculty of Engineering Science: Computer Science
\item Research group: DTAI
\item Part of the Honoursprogramme of the Faculty of Engineering Science (research track).
\item Topic: Development of an row-based type-\&-effect system for the Eff programming language
\end{cvitems}
}

\cventry{KU Leuven}{Research Assistent: efficient compilation of algebraic effect handlers}{Leuven, Belgium}{Sep. 2016 - Apr. 2017}
{\begin{cvitems}\item Faculty of Engineering Science: Computer Science
\item Research group: DTAI
\item Part of the Honoursprogramme of the Faculty of Engineering Science (research track).  My project is part of the C1 project: Algebraic Effect Handlers: Harnessing the Fundamental Power of Effects. Eff is a functional programming language that uses handlers to handle all kinds of effects. These effects could be I/O, exceptions, user-defined, etc. My task is to design, implement, benchmark and formally proof new optimisations in the Eff compiler. The compiler is written in OCaml.
\end{cvitems}
}

\cventry{Expertise centre for Digital Media (EDM), UHasselt}{Web Performance Research Internship}{Hasselt, Belgium}{Jul. 2016 - Sep. 2016}
{\begin{cvitems}\item I worked on the iMinds PRO-FLOW project.
\item My work involved creating multiple usecases to measure website performance. The main focus is on the difference between the http versions (http1.1, https, http2).
\item During the project, I had to utilise multiple servers, maintain and extend the nodejs framework used to measure website performance, and manually optimize commercial websites using PHP, JS, HTML and CSS.
\end{cvitems}
}

\cventry{Expertise centre for Digital Media (EDM), UHasselt}{Summer Research Internship Physical Computing}{Hasselt, Belgium}{Aug. 2015 - Sep. 2015}
{\begin{cvitems}\item Work on a project which focuses on the interaction between a human entity and a drone, aswell as interaction between the drone and virtual objects. This project is written in C++, used the Optitrack motion capture and a custom created drone.
\end{cvitems}
}


\end{cventries}
