\cvsection{Extracurricular Activities}

\begin{cventries}
\cventry{DjangoGirls coach}{KU Leuven}{Leuven, Belgium}{Mar. 2018 - Current}
{\begin{cvitems}\item We inspire women to fall in love with programming.
\item Django Girls organize free Python and Django workshops, create open sourced online tutorials and curate amazing first experiences with technology.
\end{cvitems}
}

\cventry{Student Representative}{KU Leuven}{Leuven, Belgium}{Sep. 2017 - Sep. 2018}
{\begin{cvitems}\item POC of Master Computer Science Engineering
\item POC of Advanced Master Artificial Intelligence
\item Member of Departmental council of Computer Science
\item Member of Department board of Computer Science
\item Member of Faculty council of Engineering Science
\end{cvitems}
}

\cventry{Coach}{CoderDojo Belgium}{Uasselt, PXL}{Sep. 2014 - Current}
{\begin{cvitems}\item Teach children how to program utilising Scratch, Python, Minecraft and Lego mindstorm.
\end{cvitems}
}

\cventry{Member}{Student Council}{UHasselt}{Aug. 2015 - Aug. 2016}
{\begin{cvitems}\item Member of Board of Education
\item Member of Faculty Council
\item Member of Board of Student Facilities
\item Member of Diversity Commission
\item Temporary representative in VVS (Vlaamse Vereniging van Studenten vzw)
\end{cvitems}
}

\cventry{Member}{Student Council}{UHasselt}{Mar. 2015 - Aug. 2015}
{\begin{cvitems}\item Member of Board of Education
\item Member of Faculty Council
\item Member of Board of Student Facilities
\end{cvitems}
}

\cventry{Student Representative}{UHAsselt}{Hasselt, Belgium}{Sep. 2013 - Jul. 2016}
{\begin{cvitems}\item Representing students interests in a Computer Science education context.
\item This meant discussing with the university in order to improve teaching, learning, assessment and academic services.
\item Representing Computer Science education for high school students
\end{cvitems}
}


\end{cventries}
